A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-12 6_validation.tex
write widening section as addendum to strategy

>>>>

Determining what the optimal distribution scheme would be is left as future work.

\paragraph{Widening}
Complementary to any of these strategies we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,d)_1 &=
\begin{cases}
\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
W(n,d)_1 & \text{ otherwise}
\end{cases}
\end{align*}
